Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

\subsection{Scale and Length}
Image scale and fish lengths were calculated for \(7,179\) of the images.
For the remaining 65 images, either the fish, the ``2'' and/or the ``3'' on the ruler were not detected.
Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
measured, using ImageJ~\cite{imagejCite}, in the same 100  test images.
% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ~\cite{imagejCite}.
In this subset of images the average error for the scale calculation
was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler. When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well. An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm). Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/54172}
  \includegraphics[width=0.49\linewidth]{images/54172_mask}
  \caption{A fish for which the masking and measurement process was highly accurate.}
  \label{fig:scale_len}
\end{figure}

>>>>

\subsection{Scale and Length}
Image scale and fish lengths were calculated for \(7,179\) of the images.
For the remaining 65 images, either the fish, the ``2'' and/or the ``3'' on the ruler were not detected.
Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
measured, using ImageJ~\cite{imagejCite}, in the same 100  test images.
% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ~\cite{imagejCite}.
In this subset of images the average error for the scale calculation
was \(0.89\%\), and the average error for the fish length calculation was \(5.55\%\).
Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler. When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well. An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm). Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/54172}
  \includegraphics[width=0.49\linewidth]{images/54172_mask}
  \caption{A fish for which the masking and measurement process was highly accurate.}
  \label{fig:scale_len}
\end{figure}
